### 2015-09-12 Paper_v2.tex
error change
probform

\documentclass[12pt]{article}
% Load packages
\usepackage{url}  % Formatting web addresses
\usepackage{ifthen}  % Conditional
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{graphicx}
\usepackage[margin=0.1pt,font=footnotesize,labelfont=bf]{caption}
\usepackage{setspace}
%\usepackage{longtable}
\usepackage{colortbl}
%\usepackage{palatino,lettrine}
%\usepackage{times}
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\usepackage[wide]{sidecap}
%\usepackage[authoryear,round,comma,sort&compress]{natbib}
\usepackage[square,sort,comma,numbers,sort&compress]{natbib}
%\usepackage[authoryear,round]{natbib}
\usepackage{supertabular}
\usepackage{simplemargins}
\usepackage{fullpage}
\usepackage{comment}
\usepackage{lineno}
%\usepackage{chicago}
\usepackage{textcomp}

%\usepackage[space]{cite}
\urlstyle{rm}

@@

\clearpage
\section*{Results}
\subsection*{Dynamically dimensioned particle swarm optimization (DdPSO).}
DdPSO is a novel meta-heuristic that combines multi-swarm based particle swarm methods with dynamically dimensioned search (Fig.\ref{fig-algorithm}).
The goal of this approach is to obtain optimal or near optimal parameters for high-dimensional complex biological systems within a pre-specified number of function evaluations. We randomly initialized a swarm of $\mathcal{K}$-dimensional particles (represented as ${x}_{i}$), wherein each of these particles corresponds to a $\mathcal{K}$-dimensional parameter vector. After initialization, the particles were grouped into different sub-swarms randomly. Thereafter within each sub-swarm ${S}_{k}$,  particles were updated according to the following rule.
\begin{eqnarray}
	\mathbf{x}_{i,j} &=&\theta_{1,j-1}\mathbf{x}_{i,j-1} + \theta_{2}\mathbf{r}_{1}\left(\mathcal{L}_{i} - \mathbf{x}_{i,j-1}\right) + \theta_{3}\mathbf{r}_{2}\left(\mathcal{GL}_{k} - \mathbf{x}_{i,j-1}\right)
\end{eqnarray}
where $\left(\theta_{1},\theta_{2},\theta_{3}\right)$ are adjustable parameters, $\mathcal{L}_{i}$ denotes the best local solution found by particle $i$ till function evaluation $j$-$1$, and
$\mathcal{GL}_{k}$ denotes the best local solution found over the population of all particles within the swarm ${S}_{k}$. The quantities $r_{1}$ and $r_{2}$ denote uniform random vectors with the same dimension as the number of unknown model
parameters ($\mathcal{K}\times{1}$). In our algorithm the parameter $\theta_{1,j-1}$ depends on the function evaluations and is controlled according to the following equation
\begin{eqnarray}
	\mathbf \theta_{1,j}&=&((\mathbf{N}-{j})*(\mathbf{w}_{max}-\mathbf{w}_{min}))/(\mathbf{N}-{1}) + \mathbf{w}_{min}
\end{eqnarray}
where $\mathbf{N}$ represents the total number of function evaluations, $\mathbf{w}_{max}$ and $\mathbf{w}_{min}$ are the maximum and minimum inertia weights respectively. While updating the particle, we made sure all dimensions of the solution represented by the particle were within bounds using a reflection boundary condition.

@@

>>>>

\documentclass[12pt]{article}
% Load packages
\usepackage{url}  % Formatting web addresses
\usepackage{ifthen}  % Conditional
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{graphicx}
\usepackage[margin=0.1pt,font=footnotesize,labelfont=bf]{caption}
\usepackage{setspace}
%\usepackage{longtable}
\usepackage{colortbl}
%\usepackage{palatino,lettrine}
%\usepackage{times}
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\usepackage[wide]{sidecap}
%\usepackage[authoryear,round,comma,sort&compress]{natbib}
\usepackage[square,sort,comma,numbers,sort&compress]{natbib}
%\usepackage[authoryear,round]{natbib}
\usepackage{supertabular}
\usepackage{simplemargins}
\usepackage{fullpage}
\usepackage{comment}
\usepackage{lineno}
%\usepackage{chicago}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{amsmath}
\DeclareMathOperator*{\argmin}{\arg\!\min}
%\usepackage[space]{cite}
\urlstyle{rm}

@@

\section*{Problem Formulation}

The problem of parameter estimation in dynamic biological systems consists of finding an optimal parameter vector that results in the best fit between the model predictions and observed experimental data.The cost function or objective that measures the goodness of fit is generally the Euclidean norm which is minimized under certain constraints. This can be mathematically expressed as follows.

\begin{equation}\label{eq:static_opt}
\begin{aligned}
& \text{minimize}
& & K(\mathbf{p})=(\sum_{i=1}^N g_i(t_i,\mathbf{x,p,u})-y_i)^2) \\
& \text{subject to}
&&\dot{x}=f(t,\mathbf{x(t,\mathbf{p}),p,u(\mathbf{t})})\\
&&&x(t_0) = x_0\\
&&&c(t,\mathbf{x,p,u}) \geqslant 0 \\
&&& \mathbf{p}^L \leqslant \mathbf{p} \leqslant \mathbf{p}^U\\
\end{aligned}
\end{equation}

where t is time, x is the state variable with an initial state x\_0 u is the input vector \, p is the parameter vector and f is the system of equations (like differential equations or set of algebraic constraints), c in the set of linear and non-linear constraints, g is the set of observables and p\textsuperscript{L} and p\textsuperscript{U} are the lower and upper bounds. Thus the problem eventually is to find {p}\textsuperscript{*} where

\begin{equation}\label{eq:static_opt_2}
\mathbf{p^{*}}= \arg\min_{p} K(\mathbf{p})
\end{equation}

\section*{Results}
\subsection*{Dynamically dimensioned particle swarm optimization (DdPSO).}
DdPSO is a novel meta-heuristic that combines multi-swarm based particle swarm methods with dynamically dimensioned search (Fig.\ref{fig-algorithm}).
The goal of this approach is to obtain optimal or near optimal parameters for high-dimensional complex biological systems within a pre-specified number of function evaluations. We randomly initialized a swarm of $\mathcal{K}$-dimensional particles (represented as ${x}_{i}$), wherein each of these particles corresponds to a $\mathcal{K}$-dimensional parameter vector. After initialization, the particles were grouped into different sub-swarms randomly. Thereafter within each sub-swarm ${S}_{k}$,  particles were updated according to the following rule.
\begin{eqnarray}
	\mathbf{x}_{i,j} &=&\theta_{1,j-1}\mathbf{x}_{i,j-1} + \theta_{2}\mathbf{r}_{1}\left(\mathcal{L}_{i} - \mathbf{x}_{i,j-1}\right) + \theta_{3}\mathbf{r}_{2}\left(\mathcal{GL}_{k} - \mathbf{x}_{i,j-1}\right)
\end{eqnarray}
where $\left(\theta_{1},\theta_{2},\theta_{3}\right)$ are adjustable parameters, $\mathcal{L}_{i}$ denotes the best local solution found by particle $i$ till function evaluation $j$-$1$, and
$\mathcal{GL}_{k}$ denotes the best local solution found over the population of all particles within the swarm ${S}_{k}$. The quantities $r_{1}$ and $r_{2}$ denote uniform random vectors with the same dimension as the number of unknown model
parameters ($\mathcal{K}\times{1}$). In our algorithm the parameter $\theta_{1,j-1}$ depends on the function evaluations and is controlled according to the following equation
\begin{eqnarray}
	\mathbf \theta_{1,j}&=&((\mathbf{N}-{j})*(\mathbf{w}_{max}-\mathbf{w}_{min}))/(\mathbf{N}-{1}) + \mathbf{w}_{min}
\end{eqnarray}
where $\mathbf{N}$ represents the total number of function evaluations, $\mathbf{w}_{max}$ and $\mathbf{w}_{min}$ are the maximum and minimum inertia weights respectively. While updating the particle, we made sure all dimensions of the solution represented by the particle were within bounds using a reflection boundary condition.

@@

\begin{table}[h]
\centering
\caption{Error Analysis.}
\label{table:Error-Analysis}
\begin{center}
\begin{tabular}{ |c|c|c|c| } 
\hline
Simulation&Concentration& Normalized Standard Error & R-Squared Value \\
\hline
\multirow{3}{4em}{FVIIa-TF level} & 5nM & 0.0367 & 0.7680\\ 
& 500pM & 0.0636 & 0.8939\\
& 50pM & 0.1204 & 0.8384\\ 
& 10pM & 0.0813 & 0.9492\\
& 5pM & 0.0574 & 0.9794\\ 
\hline
\end{tabular}
\end{center}
\end{table}
